The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-07 paper/main.tex
Added a "Linux Law" section.
Started on summary statistics.

% SEng 5852 - Spring 2013 White Paper Review
\documentclass{proc}
\usepackage{graphicx}
\setlength\parindent{0pt}

@@

@@

\section{Methods}

\section{Results}
\subsection{Hypotheses}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}

>>>>

% SEng 5852 - Spring 2013 White Paper Review
\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\setlength\parindent{0pt}

@@

This is, ultimetely, a proof of ``Linus Law"\cite{raymond1999cathedral} in the context of GitHub. In other words, the more exposure the code gets (in terms of forks), the easier bugs will be to find and fix.

@@

\section{Methods}
Data collection was done using the GitHub REST API\footnote{http://developer.github.com/v3/}. A random selection of 1000 repositories was selected using the following algorithm:\footnote{https://github.com/kevinpeterson/github-process-research/blob/master/code/research.py}

\begin{algorithmic}
\While{$i < 1000$} 
\State $i \gets i + 1$
\State $word \gets random(word\_list)$
\State $repos \gets git\_search(word)$
\State $j \gets random(0...size(repos))$
\State $repo \gets repos_j$
\State \Call{process}{repo}
\EndWhile
\end{algorithmic}\footnote

$\displaystyle\frac{\sum\limits_{i=1}^{n} f( \left\{{i_j,i_{j+1},...,i_{j+k}  }\right\} ) } {n} $.

\section{Results}

\subsection{Summary Statistics}
\begin{table}[!ht]
\begin{center}
\caption{GitHub Summary Statistics}
\begin{tabular}{rrrrrrr}
\hline
Variable & Mean & Min & Max & Std. Dev. \\
\hline
\input{summary_statistics}
\hline
\end{tabular}
N = 100 Repositories
\end{center}
\end{table}

\subsection{Hypotheses}
\emph{Hypothesis 1: As the number of Watchers increase, the number of Repository Forks will increase.}\\
\includegraphics[height=3in,width=3in]{images/watcher_forks_scatterplot.png}
